%Two resources useful for abstract writing.
% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf %https://writingcenter.gmu.edu/guides/writing-an-abstract
\chapter*{\center \Large  Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace all text with your text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This project developed LiveSpot, a real-time location-based news tracking and verification platform designed to combat misinformation through location-verified community reporting and news aggregation. The platform addresses the growing problem of fake news and fragmented information sources by creating a unified application where users can report real-time events, verify ongoing incidents, and access curated news from multiple external sources within their local communities.

The application was implemented using Flutter framework for cross-platform compatibility across Android, iOS, and web platforms, integrated with Firebase for real-time messaging and Django REST API for backend services. Key implemented features include GPS-based location verification for posts, community-driven honesty scoring system, intelligent threading that automatically groups related events, crowd-sourced event status verification through "still happening" votes, comprehensive news aggregation with external API integration, interactive mapping using OpenStreetMap, and AI-powered messaging suggestions using Google Gemini API. The system employs location-based authentication to ensure post authenticity and implements automatic content threading to enable collaborative event tracking.

The development resulted in a fully functional news tracking and verification platform capable of real-time event reporting with location verification, successful integration of multiple external news sources, implementation of community-based credibility systems, and deployment across multiple platforms using a single codebase. The platform successfully demonstrates cross-platform functionality, real-time data synchronization, and effective integration of location services with news tracking features. Testing confirmed reliable performance across different devices and operating systems, with successful implementation of all core verification and aggregation features.


~\\[1cm]
\noindent % Provide your key words
\textbf{Keywords:} Misinformation detection, Location-based authentication, Flutter cross-platform development, Real-time event verification, Community-driven journalism\\[0.5 cm]
\noindent
\textbf{GitHub Repository:} \url{https://github.com/username/livespot-app}

\vfill
